\documentclass[letterpaper,10pt]{article}
% \usepackage{fullpage}
\usepackage[top=2cm,left=2cm,right=3cm,nohead,nofoot]{geometry}
\usepackage[pdfborder={0 0 0}]{hyperref}
\textheight=9in
\pagestyle{empty}

\begin{document}
\begin{center}
  {\LARGE \bf Nelson Elhage}\\
  {\large
    Cambridge, MA \\
%    285 3rd St Apartment 511 \\
%    Cambridge, MA 02139 \\
%    (781) 929-7843 \\
  }
  781-929-7843 \\
  \url{nelhage@nelhage.com} \\
  Blog: \url{http://blog.nelhage.com/} \\
  Github: \url{http://github.com/nelhage/}
\end{center}

\section*{Education}
\vspace*{-0.2cm}
\begin{itemize}
  \item \textbf{Massachusetts Institute of Technology}, Cambridge, MA
    \\ Bachelor of Science in Electrical
    Engineering and Computer Science, June 2009 \\
    GPA 4.9/5.0
    \vspace*{-0.2cm}
%    \begin{itemize}
%      \item Chairman, Educational Studies Program, a student-run
%        high school outreach program, 2006-2007
%      \item Chairman, Student Information Processing Board, 2009
%    \end{itemize}
  \item \textbf{Roxbury Latin School}, West Roxbury, MA \\ 2001-2005,
    Graduated {\em Summa Cum Laude} June 2005 with a 4.0 GPA
    % Received National Merit Scholar award, one of 2500 students nationwide.
\end{itemize}

\vspace*{-0.7cm}
\section*{Work experience}
\vspace*{-0.2cm}
\begin{itemize}
\item\textbf{Oracle}, Cambridge MA -- August 2011-present -- Architect \\
  \textbf{Ksplice}, Cambridge MA -- June 2009-July 2011 -- Employee \#1, Principal Engineer \\
  {\small(Ksplice was acquired by Oracle in July 2011)} \\
  Core developer on technology for creating and applying rebootless
  updates to the Linux kernel. \\
  Developed and maintained automated build and test infrastructure for
  thousands of kernel versions. \\
  Developed and maintained services to distribute updates and
  monitor customer deployments.
  \item\textbf{VMware}, Palo Alto, CA --
    Summer 2008 -- Member of Technical Staff, Intern \\
    Extended support for VMware's next-generation virtual machine
    communication infrastructure.
%   \item\textbf{One Laptop Per Child}, Cambridge, MA \\
%     Summer 2007, Software Developer (Intern) \\
%     Worked on infrastructure web applications for laptop tracking and
%     anti-theft system.
%  \item \textbf{MIT Information Services \& Technology}, Cambridge, MA
%    \\
%    January, 2006, Software Developer \\
%    Implemented Jabber support for the owl instant messenger client.
  \item \textbf{Best Practical Solutions}, Somerville, MA --
    Summer 2006 -- Software Developer (Intern) \\
    Developer for Hiveminder (\url{http://hiveminder.com}) and Jifty,
    a Perl web application framework.
%  \item \textbf{Tangible Media Group}, Media Lab, MIT \\
%  Fall Term 2005, assistant system administrator and developer. \\
%  Set up internal project server and disk array (Xen virtual
%    machines hosting subversion, NFS, Apache, and other services)
%  \item Developed new GUI layer for lab projects
%  \item Re-architected Sandscape codebase
%    (http://tangible.media.mit.edu/projects/sandscape/).
%   \item \textbf{Geode Capital Management, LLC}, Boston, MA \\
%   Summer 2005, Software Developer (Intern) \\
%   Developed internal system to automate downloading and access of {\em
%     Yahoo! \textregistered News} headlines and electronic SEC
%   filings. Analyzed data using the R statistical programming language
\end{itemize}

\vspace*{-0.7cm}
\section*{Other Experience}
\vspace*{-0.2cm}
\begin{itemize}
  \item \textbf{Other projects} \\
    \vspace*{-0.5cm}
    \begin{itemize}
    \item Developed \url{http://livegrep.com}, providing real-time
      interactive regular expression search over $>$450MB of source
      code.
    \item Developed Virtunoid, a proof-of-concept
      guest$\rightarrow$host privilege escalation exploit against
      KVM. Presented at Black Hat USA and Black Hat UAE
      2011. (\url{http://github.com/nelhage/virtunoid})
    \item bemu, a JIT compiler implementing the ``Beta'' CPU, a
      fictional CPU used by several MIT
      courses. (\url{http://github.com/nelhage/bemu})
    \item Developer and former lead maintainer of Barnowl IM client
      (\url{http://barnowl.mit.edu})
      % \item Former developer for Adium X (http://adiumx.com) and Growl
      %   (http://growl.info).
      % \item Contributed significant patches to bitlbee
      %  (http://bitlbee.org)
    \end{itemize}

  \item \textbf{Relevant coursework}
  \begin{itemize}
      \item Teaching Assistant, 6.828 {\em Operating Systems Engineering}, Fall 2007
      \item 6.035 {\em Computer Language Engineering} Fall 2007 \\
        Implemented an optimizing and data-parallelizing compiler for a
        C-like language.
%      \item 6.170 {\em Laboratory in Software Engineering} Spring 2006 \\
%        Designed and implemented an Antichess engine, UI and AI with a three-man team
      \item 6.828 {\em Operating Systems Engineering} Fall 2006 \\
        Implemented a minimal unix-style OS kernel and userspace
%      \item 6.891 {\em Adventures in Advanced Symbolic Programming} Spring 2006
      % \item Participed in 2006 Maslab competition -- Programmed
      % autonomous vision-based robot, placing second out of 14 teams.
  \end{itemize}
\end{itemize}

\section*{Skills}
\vspace*{-0.2cm}
\begin{itemize}
\item Proficient in C, Python, Javascript, C++
\item Comfortable with Perl, HTML, CSS, Lisp/Scheme, Java, SQL, Haskell
\item Comfortable with basic UNIX system administration.
% \item Familiar with \LaTeX, HTML, CSS
% \item Comfortable with UNIX system administration.
  % Proficient in Perl, C, Lisp/Scheme, Java,
  % Haskell, SQL, \LaTeX, CSS. Familiar with Python, C++, OCaml, R, PHP

  % \item Unix system administration -- bash command-line and scripting,
  %  Debian Linux, PostgreSQL, Apache, MySQL, Subversion, CVS
\end{itemize}

% TODO: Black Hat talk?

\end{document}
